### 2020-01-04 cv_models.tex
latest PDF
still working on CV
placeholders for CV images

@@

\begin{figure}
  \centering
  \includegraphics[scale=0.30]{img/vgg-alpha-layers.png}
  \label{fig:vgg-alpha-layers}
    \caption{Power law exponent $\alpha$ vs layer for VGG11 and VGG19. }
\end{figure}

>>>>

\paragraph{Empirical Metrics vs Test Accuracies for VGG}

@@

ADD PLOTS FOR

pNorm and ResNet
pNorm and ResNet (ImageNet1K all models)
pNorm and DenseNet

\paragraph{Correlations and Information Flow in CV Models}

\begin{figure}[t]
    \centering

    \subfigure[ VGG ]{
        \includegraphics[width=4.1cm]{img/vgg-alpha-layers.png}
        \label{fig:vgg-alpha-layers}
    }
    \qquad
    \subfigure[ ResNet ]{
        \includegraphics[width=3.8cm]{img/resnet-alpha-layers.png}
        \label{fig:resnet-alpha-layer}
    }
    \qquad
    \subfigure[ DenseNet ]{
        \includegraphics[width=4.1cm]{img/densenet-alpha-layers.png}
        \label{fig:densenet-alpha-layer}
    }
    \caption{Power law exponent $\alpha$ vs layer for VGG, ResNet, and DenseNet models}
    \label{fig:vgg-alpha-layers}
\end{figure}
